---
title: "p8105_hw1_vas2145"
output: github_document
date: "2023-09-19"
---
## Problem 1


```{r}
library(moderndive)
library(tidyverse)
```

```{r}
data("early_january_weather")
  nrow(early_january_weather)
  ncol(early_january_weather)
  mean_temp <- mean(pull(early_january_weather, temp))
  mean_temp
```

Load the libraries and dataset. The `early_january_weather` dataset contains  `r ncol(early_january_weather)` columns of  `r nrow(early_january_weather)` rows. Variables include the location the temperature reading was taken (EWR), the time (including `year`, `month`, `day`, `hour`), the temperature, and detailed weather conditions (`humid`, `wind`, `precipitation`, etc.) All recordings were taken in January of 2013. The mean temperature of recordings is `r mean_temp` degrees.

### Visualizing temperature as a function of time, coded by humidity
```{r}
ggplot(early_january_weather,
  aes(x= time_hour, y = temp, color = humid)) +
  geom_point()

ggsave("Temperature Scatterplot.png")

```

##Problem 2

###Create a dataframe and sample
```{r}
homework_df = tibble(
  random_sample = rnorm(10),
  vec_logical = rnorm(10) > 0,
  vec_char = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
  vec_factor = factor(c("level 1", "level 2", "level 3", "level 1", "level 2", "level 3", "level 1", "level 2", "level 3", "level 1")))
```

```{r}
mean_random_sample <- mean(pull(homework_df, random_sample))
mean_vec_logical <- mean(pull(homework_df, vec_logical))
mean_vec_char <- mean(pull(homework_df, vec_char))
mean_vec_factor <- mean(pull(homework_df, vec_factor))
```

Taking the mean of each variable in the dataset works for `mean_random_sample` and `mean_vec_logical`.

as.numeric(pull(homework_df,vec_logical))
as.numeric(pull(homework_df,vec_char))
as.numeric(pull(homework_df,vec_factor))

